%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Paul Hadfield
\documentclass[line]{resume}
\usepackage[
top    = 1.50cm,
bottom = 1.00cm,
left   = 1.50cm,
right  = 2.75cm]{geometry}
\usepackage{hyperref}
%\setlength{\topmargin}{-1cm}

%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Paul Hadfield}
\begin{resume}

    %__________________________________________________________________________________________________________________
    % Contact Information
    \section{\mysidestyle Contact\\Information}

    Based in London SE19, UK.              \hfill \url{mailto:hadfieldp@gmail.com}         \vspace{0mm}\\\vspace{0mm}%
                                           \hfill \url{https://github.com/phad}            \vspace{0mm}\\\vspace{0mm}%
                                           \hfill \url{https://keybase.io/hadfieldp}       \vspace{0mm}\\\vspace{0mm}%
                                           \hfill \url{tel:44-7973-297961}                 \vspace{0mm}\\\vspace{-4.5mm}%

    %__________________________________________________________________________________________________________________
    % Career Objective
    \section{\mysidestyle Objective}

    A leading developer role in a tight-knit team, building products that improve the safety, security and privacy of
    users and their data.  I'm looking for a software group that offers intellectual challenge, technical variety, and
    the opportunity to have a meaningful impact on others.

    %__________________________________________________________________________________________________________________
    % Profile
    \section{\mysidestyle Profile}

    I am a Software Engineer with over 25 years of professional development experience.  I currently work at Google in
    the Android group, on the server stack behind Android and WhatsApp backup.  Our service manages an \textsl{xx} EiB estate of
    user data for over a billion users. My earlier experience at Google includes six years in the security team, where
    I worked on Certificate Transparency - an effort to increase trust in the Web PKI and to detect CA malfeasance or
    compromise.  In 2006 I was one of Google's earliest SWE hires in the new London engineering office.
    During 2020-2021 I worked in Monzo Bank's security group, as a Backend Engineer in the Security Platform squad.  I
    also have start-up experience from two years spent at Songkick, one of London's first Silicon Roundabout start-ups.

    %__________________________________________________________________________________________________________________
    % Selected Projects
    \section{\mysidestyle Selected Projects}

    In the \textsl{Android Onboarding} group, I work on Moscato - a modern Java service that underpins device backups
    for Android users. It serves millions of queries-per-second to billions of user devices. I'm responsible for the
    roll-out of new gRPC APIs to clients, for our integration with Legal Takeout, and for defining a new process for
    disaster recovery.  I work closely with SREs and client-side engineers.  I've contributed to GMS Core and the
    Android Open-source project.  My current project brings our server stack into compliance with the EU's Digital
    Markets Act, DMA5(2).

    For the \textsl{Google Transparency Report} I built a system to ingest millions of SSL certs from all known CT Logs,
    cryptographically verifying the Logs' correctness in the process.  I designed the storage and serving layers, and
    implemented a front-end to allow users to search for certificates that might be served on their domains.  This
    helps users understand whether mis-issuance of certs has occurred that could impact the safety of their users. The
    rewrite I did in 2019 using Spanner Queues hugely improved throughput and reliability of the search indexing aspect
    downstream of ingestion.  I wrote a monitoring tool using the ingested corpus of certs.  This checked for cert
    mis-issuances across Google's entire domain estate.  During early testing, my monitor caught a genuine
    \url{google.com} cert mis-issuance by Thawte - a reseller of Symantec - which got coverage in the tech press.  This
    contributed to the eventual distrust of Symantec's roots and the closure of their certs business.

    At \textsl{Monzo}, I extended an existing alerting system to ingest CVE feeds into an internal incident database.
    Later I extended it again to ingest findings from the third-party Snyk service, and assign vulnerability alert tickets
    to the appropiate team. I worked on systems to define and enforce staff policies for access to internal systems. I
    built a system using gRPC service introspection to assist in policing engineers' direct access to internal RPC
    services.  I was on the Security Operations rota, with duties including investigation and resolution of alerts
    from a variety of detection systems.  This role included mentoring new operations staff and writing playbook
    material.

    As part of \textsl{Google's AdSense Plugin for Wordpress} I implemented a feature to automatically place Ad Slots
    in users' Wordpress pages in locations recommended by an ML system. I did the back-end and front-end dev work.  To
    determine if the recommendations were effective I designed an A/B experiment and performed a statistical analysis
    of monetization uplift.  I then refocused the product to emphasize the aspects that performed best.

    I built the back-end services for \textsl{Songkick's `Detour'} crowdfunded concert product. I enjoyed
    being part of a small, agile dev team working in the early product discovery phase, with rapid cycles of building
    out new features, launching experimentally, measuring their performance through A/B tests and user studies and
    analysing data collected from the product. The ideas behind `Detour' were quite disruptive, and it was exciting to
    see how the product resonated with users.

    \pagebreak

    %__________________________________________________________________________________________________________________
    % Professional Experience
    \section{\mysidestyle Professional\\Experience}

    \textbf{Google Inc.}, London, UK \vspace{2mm}\\\vspace{1mm}%
    \textbf{Senior Software Engineer} \hfill \textbf{June 2021 -- current}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item Android Backup \& Restore server development - Java, Guice, AppsFramework, Boq, Spanner, Blobstore, SQL,
        FlumeJava, Borg/Sigma, Monitoring, SLOs/SLIs with SREs, on-call rota
        \item Android Backup \& Restore client development - Java, Android, GMScore, Android Open-Source Project, adb
        \item Golang readability reviewer (2017-2019, 2021-2023, volunteer basis)
        \item 20\% project -- Android Security 'DroidzInspect', checking apps for OWASP MASVS violations - Python
    \end{list2}\vspace{-1.5mm}

    \textbf{Monzo Bank Ltd.}, London, UK \vspace{2mm}\\\vspace{1mm}%
    \textbf{Backend Engineer} \hfill \textbf{February 2020 -- May 2021}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item Backend microservice development - Golang, Cassandra, Proto, Kubernetes, AWS
        \item Front end tool development - Javascript, React, Next.js
        \item Security Operations rota - internal security advice/support, resolving alerts, various approval tasks
    \end{list2}\vspace{-1.5mm}

    \textbf{Google Inc.}, London, UK \vspace{2mm}\\\vspace{1mm}%
    \textbf{Senior Software Engineer} \hfill \textbf{November 2013 -- January 2020}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item Trillian and Key Transparency (KT) - occasional open-source contributions (Golang), 2017-2018
        \item Certificate Transparency (CT) - Log Ingestion and Search (Golang, Python, SQL, Spanner, ST, Flume-C++, Pubsub2, Borg; on-call), 2016-2019
        \item Public work: contributions to Chromium (C++) and IETF's RFC6962-bis (CT v2), 2016-2018
        \item Transparency Report, HTTPS Certificate Search (Java, Javascript, Closure, Jasmine, HTML/CSS), 2016
        \item Certificate Transparency - Compliance Monitoring (C++11, Spanner, SQL, Borg, Proto, Stubby; on-call), 2015-2016
        \item Google AdSense Plugin (Java, Guice, Producers, FlumeJava, Javascript, Python, SQL, R), 2013-2014
    \end{list2}\vspace{-1.5mm}

    \textbf{Songkick.com, Inc.}, London, UK \vspace{2mm}\\\vspace{1mm}%
    \textsl{Senior Software Engineer} \hfill \textbf{August 2011 -- September 2013}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item Songkick Mobile Team, both iPhone and Android (Objective-C, iOS6, Java, Android, Tech Lead), 2013
        \item Data Science Team (Ruby, Python, Java, Hadoop/Pig, MongoDB, AWS S3, MySQL, Tech Lead), 2013
        \item Songkick Detour (Ruby, Rails 3, MongoDB, MySQL, AWS EC2), 2012-2013
        \item Songkick for Android - both client and server work (Java, Android, Ruby, Tech Lead), 2012
        \item Various back-end services for songkick.com (Ruby, MySQL, Redis, MongoDB), 2011-2012
        \item www.songkick.com features (Ruby, Rails, MySQL), 2011
    \end{list2}\vspace{-1.5mm}

    \textbf{Google Inc.}, London, UK \vspace{2mm}\\\vspace{1mm}%
    \textsl{Software Engineer} \hfill \textbf{January 2006 -- August 2011}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item Android Maps Local 'Hotpot' (Java,  Android 4.0), 2011
        \item Android Market (Java,  Google server-side and Android 3.0), 2011
        \item Mobile App Search (Java, C++, STL, Megastore, ST, Borg, FlumeJava; on-call), 2009-2010
        \item Google Mobile App (Symbian/portable C++, S60 3rd \& 5th Edition, Tech Lead), 2008-2009
        \item Various unreleased products, Symbian/portable C++, S60 3rd Edition, various phones), 2006-2007
    \end{list2}\vspace{-1.5mm}

    \textbf{Symbian Software Ltd.}, London, UK \vspace{2mm}\\\vspace{1mm}%
    \textsl{Principal Software Engineer} \hfill \textbf{May 1999 -- December 2005}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item SyncML Device Management (DM)(C++, Symbian 9.1, Tech Lead, Architect), 2003-2005
        \item Representative for Symbian to Open Mobile Alliance, DM working group, 2004-2005
        \item HTTP Client (C++, Symbian 6.1-8.0, Tech Lead), 2001-2003
        \item WAP Browser (C++, Symbian 6.0-7.0), 2000-2001
    \end{list2}\vspace{-1.5mm}

    \textbf{Logica UK Ltd.}, Defence Division, London, UK \vspace{2mm}\\\vspace{1mm}%
    \textsl{Analyst/Programmer, Consultant} \hfill \textbf{October 1994 -- April 1999}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item Land Formation Model, a parallel discrete event simulation for DERA (C++/Solaris/CORBA), 1996-1998
        \item STAMGEN, land-based sensor simulation for DERA (C++/Solaris/ILOG Views/Geodetics), 1994-1996
    \end{list2}\vspace{-1.5mm}

    \textbf{Thorn EMI Electronics Ltd.}, Feltham, Middlesex, UK \vspace{2mm}\\\vspace{1mm}%
    \textsl{Sponsored Student Engineer} \hfill \textbf{September 1990 -- August 1991, vacations 1992/93}\vspace{-3mm}\\\vspace{-1mm}%
    \vspace{-1.5mm}


    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle Education}

    \textbf{University of Cambridge}, Churchill College, Cambridge, UK \vspace{2mm}\\\vspace{1mm}%
    \textsl{BA (Hons)} Electrical and Information Sciences (II.I)\hfill \textbf{ September 1991 -- June 1994}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item Y3 (II.I): Analogue and Digital Electronics, Non-Linear Systems,
            Mathematics, Communications, Information Engineering, Computer Systems, Project: `Stereo Vision with Finger
            Pointing for a Man-Machine Interface'
        \item Y2 (I): Circuits, Control Systems, Materials, Electronics, Computing, Thermodynamics, Fluid Mechanics
        \item Y1 (II.I): Electronics, Mathematics, Structures, Mechanics, Materials,  Drawing
    \end{list2}\vspace{-1.5mm}

    \textbf{Coursera}, \url{www.coursera.org}\hfill \textbf{ 2012 -- 2017}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item Technical courses: Bitcoin and Cryptocurrency Tech; Cryptography I; Statistics I, Introduction to Data
              Science; The Data Scientist's Toolbox; R Programming; Getting and Cleaning Data; Exploratory Data Analysis
        \item Non-technical courses: Technology of Music Production; Art of Music Production; Write Like Mozart
    \end{list2}\vspace{-1.5mm}

    \textbf{Beauchamp College}, Leicester, UK\hfill \textbf{ September 1986 -- July 1990}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item 2 `S' Levels (1, 2); 4 `A' Levels (AAAB), 10 GCSEs: (6A, 3B, C)
    \end{list2}\vspace{-1.5mm}

    %__________________________________________________________________________________________________________________
    % Awards
    \section{\mysidestyle Selected Awards}

    London \& Southeast Craft Beer Competition 2017 Gold Medal (Brown and Bitter category)            \vspace{0.5mm}\\%
    Google TI Award 2016; Peer Bonus 9x 2008-2023; Spot Bonus, 2015, 2008, 2021, 2022                 \vspace{0.5mm}\\%
    Institute Of Electrical Engineers Jubilee Scholarship to University, 1990                         \vspace{0.5mm}\\%
    Thorn EMI Electronics Ltd. `thick sandwich' sponsorship to University, 1990

    %__________________________________________________________________________________________________________________
    % Publications
    \section{\mysidestyle Publications}

    Cipolla, R., Hadfield, P.A., Hollinghurst, N.J.,
    ``Uncalibrated Stereo Vision with Pointing for a Man-Machine Interface",
    \textsl{Proceedings of IAPR Workshop on Machine Vision Applications}, pp163 - 166, Kawasaki, 1994.

    %__________________________________________________________________________________________________________________
    % Affiliations
    \section{\mysidestyle Affiliations and Responsibilities}

    Member of United Tech and Allied Workers union, a branch of the CWU, 2022 --                            \vspace{0.5mm}\\%
    Member of South London Maker Space, 2021 --                                                             \vspace{0.5mm}\\%
    Baritone sax and committee chair, King Groovy \& the Hornstars band \url{http://hornstars.com}, 2015 -- \vspace{0.5mm}\\%
    Member of the Incorporated Society of Musicians, 2019 --                                                \vspace{0.5mm}\\%
    Member of Open Rights Group, 2010 --                                                                    \vspace{0.5mm}\\%
    Member of CAMRA, 2004 -- , and volunteer podcast editor, 2020 -- 2022                                   \vspace{0.5mm}\\%
    Member of the IET, 1991 -- present; registered as CEng 2005

    %__________________________________________________________________________________________________________________
    % Hobbies/Interests
    \section{\mysidestyle Hobbies and Interests}

    Music (sax, piano \& hammond organ), recording (\url{http://soundcloud.com/hadfieldp}), home-brewing, hacking,
    electronics (built a Picade bartop arcade machine, a modular synth and now working on fx pedals), running, family.

    %__________________________________________________________________________________________________________________
    % References
    \section{\mysidestyle References}

    Available on request.

    %__________________________________________________________________________________________________________________
    % Last Update
    \section{\mysidestyle Last Updated: 2023-11-18T13:29:30+0000}

%______________________________________________________________________________________________________________________
\end{resume}
\end{document}

%______________________________________________________________________________________________________________________
% EOF
